Multi-resolution Neural Field Estimation

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
suggestion for cutting

where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted $v_t\left(\mathbf r\right)$. Synaptic dynamics are included through the parameter $\xi=\left(1-\frac{ T_s}{\tau}\right)$, where $\tau$ is the synaptic time constant and $T_s$ is the sampling time. The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$. The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}. The term $e_t(\mathbf r)$ is an i.i.d. disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}. The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$. A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function. \ken{Doing something just for computational efficiency only might be weak ... is there other work we can reference that makes the linearity assumption? ... or are there practical situations when this known to be a good approximations?} The observation equation describing the electrophysiological recordings is given by

>>>>

where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted $v_t\left(\mathbf r\right)$. Synaptic dynamics are included through the parameter $\xi=\left(1-\frac{ T_s}{\tau}\right)$, where $\tau$ is the synaptic time constant and $T_s$ is the sampling time. The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$. The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}. The term $e_t(\mathbf r)$ is an i.i.d. disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$\cut{~\cite{Rasmussen2005}}. The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$. A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function. \ken{Doing something just for computational efficiency only might be weak ... is there other work we can reference that makes the linearity assumption? ... or are there practical situations when this known to be a good approximations?} The observation equation describing the electrophysiological recordings is given by
